The \dealii{} Library, Version 9.0

### 2018-04-06 9.0/paper.tex
Remove emacs macros from bottom of file.
This is now deprecated and emacs warns about it.
Minor language edits seen at first glance and without actual reading.

\item
  A dedicated differentiation module had been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivates of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.

\item
  Support for complex-values vectors is now at the same level as real-valued
  vectors.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\item
  A dedicated differentiation module has been created to provide support for
  automatic and symbolic differentiation. Automatic differentiation is a set of
  technique to evaluate the derivates of a function defined by a compute
  program. Currently the Adol-C and Sacado libraries are supported through a
  unified interface. In practice, this support means that Adol-c and Sacado
  data types can be used in the \texttt{FEValues} and \texttt{FEValuesViews}
  to represent degree-of-freedom values.

\item
  Support for complex-valued vectors is now at the same level as real-valued
  vectors.

@@
